Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-10-23 main.tex

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[3]{Department of Biomaterials, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[4]{University of Potsdam, Institute of Physics and Astronomy, Potsdam-Golm, 14476, Germany}
%\affil[2]{Affiliation, department, city, postcode, country}
\affil[5]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, Jyv{\"a}skyl{\"a}, 40014 , Finland}
\affil[6]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[7]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[8]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[9]{Universit{\'e} Paris Cit{\'e}, UFR Sciences du Vivant, Paris, 75013, France}
\affil[10]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[11]{no affiliation}
\affil[12]{Institute of Biological Information Processing: Structural Biochemistry (IBI-7), Forschungszentrum Jülich, 52428 Jülich, Germany}
\affil[13]{ariadne.ai GmbH (Germany), Häusserstra{\ss}e 3 Heidelberg 69115, Germany }
\affil[14]{Department of Physical Chemistry of Drugs and Faculty of Pharmacy, Comenius University Bratislava, 832 32 Bratislava, Slovakia}
\affil[15]{Institute of Organic Chemistry and Biochemistry of the Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2,  Prague, CZ-16610, Czech Republic}
\affil[16]{School of Pharmacy, University of Eastern Finland, 70211 Kuopio, Finland}
\affil[17]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[18]{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[19]{Department of Chemistry, University of Bergen, 5020 Bergen, Norway}
\affil[20]{Computational Biology Unit, Department of Informatics, University of Bergen, 5020 Bergen, Norway}
\affil[21]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}
\affil[22]{Department of Applied Physics, Faculty of Physics, University of Santiago de Compostela, Santiago de Compostela, E-15782, Spain}
\affil[23]{MD.USE Innovations S.L., Edificio Emprendia, 15782 Santiago de Compostela, Spain}
\affil[24]{VTT Technical Research Centre of Finland, Espoo, Finland}
\affil[25]{Hochschule Mannheim, University of Applied Sciences, Mannheim, Germany}
\affil[26]{Institut Charles Gerhardt Montpellier (UMR CNRS 5253), Universit{\'e} Montpellier, Place Eug{\`e}ne Bataillon, 34095 Montpellier, Cedex 05, France}
\affil[27]{Heidelberg University Biochemistry Center, 69120 Heidelberg, Germany}
\affil[28]{Department of Physics, University of Helsinki, FI-00014 Helsinki, Finland}
\affil[29]{IBCP CNRS, UMR 5086 7, Lyon, France}

>>>>

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[3]{Department of Biomaterials, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[4]{University of Potsdam, Institute of Physics and Astronomy, Potsdam-Golm, 14476, Germany}
%\affil[2]{Affiliation, department, city, postcode, country}
\affil[5]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, Jyv{\"a}skyl{\"a}, 40014 , Finland}
\affil[6]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[7]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[8]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[9]{Universit{\'e} Paris Cit{\'e}, UFR Sciences du Vivant, Paris, 75013, France}
\affil[10]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[11]{no affiliation}
\affil[12]{Institute of Biological Information Processing: Structural Biochemistry (IBI-7), Forschungszentrum Jülich, 52428 Jülich, Germany}
\affil[13]{ariadne.ai GmbH (Germany), Häusserstra{\ss}e 3 Heidelberg 69115, Germany }
\affil[14]{Department of Physical Chemistry of Drugs and Faculty of Pharmacy, Comenius University Bratislava, 832 32 Bratislava, Slovakia}
\affil[15]{Institute of Organic Chemistry and Biochemistry of the Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2,  Prague, CZ-16610, Czech Republic}
\affil[16]{School of Pharmacy, University of Eastern Finland, 70211 Kuopio, Finland}
\affil[17]{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida 33612, United States of America}
\affil[18]{Center for Global Health and Infectious Diseases Research, Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida 33612, United States of America}
\affil[19]{Department of Chemistry, University of Bergen, 5020 Bergen, Norway}
\affil[20]{Computational Biology Unit, Department of Informatics, University of Bergen, 5020 Bergen, Norway}
\affil[21]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}
\affil[22]{Department of Applied Physics, Faculty of Physics, University of Santiago de Compostela, Santiago de Compostela, E-15782, Spain}
\affil[23]{MD.USE Innovations S.L., Edificio Emprendia, 15782 Santiago de Compostela, Spain}
\affil[24]{VTT Technical Research Centre of Finland, Espoo, Finland}
\affil[25]{Hochschule Mannheim, University of Applied Sciences, Mannheim, Germany}
\affil[26]{Institut Charles Gerhardt Montpellier (UMR CNRS 5253), Universit{\'e} Montpellier, Place Eug{\`e}ne Bataillon, 34095 Montpellier, Cedex 05, France}
\affil[27]{Heidelberg University Biochemistry Center, 69120 Heidelberg, Germany}
\affil[28]{Department of Physics, University of Helsinki, FI-00014 Helsinki, Finland}
\affil[29]{IBCP CNRS, UMR 5086 7, Lyon, France}
